### 2018-08-01 README.Rmd
ange name to mixchar

[![Build Status](https://travis-ci.com/smwindecker/deconvolve.svg?branch=master)](https://travis-ci.org/smwindecker/deconvolve)
[![codecov](https://codecov.io/gh/smwindecker/deconvolve/branch/master/graph/badge.svg)](https://codecov.io/gh/smwindecker/deconvolve)
[![repo status](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

@@

You can install `deconvolve` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("smwindecker/deconvolve", build_vignettes = TRUE)
```
## Basic use

Data from thermogravimetric analysis is usually exported as mass loss with temperature. An example dataset for the species *Juncus amabilis* is included in the package:
```{r}
library(deconvolve)
head(juncus)
```

@@

You can see the full worked example in the vignette, which you can access on the or in R:
```{r}
vignette('deconvolve')
```

This is still a work in progress! If you see any mistakes, or find that the code is not functioning well on your data, let us know by logging a bug on the [issues page](http://www.github.com/smwindecker/deconvolve/issues).

>>>>

[![Build Status](https://travis-ci.com/smwindecker/mixchar.svg?branch=master)](https://travis-ci.org/smwindecker/mixchar)
[![codecov](https://codecov.io/gh/smwindecker/mixchar/branch/master/graph/badge.svg)](https://codecov.io/gh/smwindecker/mixchar)
[![repo status](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

@@

You can install `mixchar` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("smwindecker/mixchar", build_vignettes = TRUE)
```
## Basic use

Data from thermogravimetric analysis is usually exported as mass loss with temperature. An example dataset for the species *Juncus amabilis* is included in the package:
```{r}
library(mixchar)
head(juncus)
```

@@

You can see the full worked example in the vignette, which you can access on the or in R:
```{r}
vignette('mixchar')
```

This is still a work in progress! If you see any mistakes, or find that the code is not functioning well on your data, let us know by logging a bug on the [issues page](http://www.github.com/smwindecker/mixchar/issues).

### 2018-08-01 manuscript/manuscript.Rnw
ange name to mixchar

\section*{Title}
deconvolve: An R package for the deconvolution of thermal decay curves

@@

\section*{Introduction}
Plant cell wall biomass is composed of a range of different types of carbon. Ecologists can use these proportions of biomass carbon as functional traits, enabling us to make generalisations about species' effects on ecosystem processes such as litter decomposition, which links plant biomass to the global carbon cycle \citep{cornwell2008}. Biofuels researchers use proportions of biomass carbon types to estimate kinetic decay parameters of species' tissue. Traditional methods for calculation of lignocellulosic biomass involve wet chemistry assays for carbon component analysis are time-consuming and adversely impact the environment through use of sulfuric acid and acetic anhydride, among other chemicals. Thermogravimetric analysis (TGA) is an alternative method, already in use among biofuels researchers, to approximate these carbon compounds from mass loss data obtained by heating a biomass sample (in a $N_2$ environment, termed pyrolysis). \\
\\
Mass loss during pyrolysis can be regarded as the sum of the degradation of the main components of the sample \textemdash hemicelluloses, cellulose, and lignin \citep{hu2016,cheng2015,perejon2011,orfao2001,muller-hagedorn2007}. Therefore, the multi-peaked rate of mass loss curve (derivative of mass loss curve) can be mathematically separated, or deconvolved, with a mixture model into individual peaks \textemdash each representing a single primary component. This method has been validated by studies comparing estimates to experimental measurements \citep{yang2006}. Plant trait measurement is guided by the principle of standardised, widely reproducible methods \citep{perez-harguindeguy2013}, but much of the published literature use commercial software to deconvolve the rate of mass loss curve \citetext{for example OriginPro \citealp{chen2017}, PeakFit \citealp{perejon2011}, Fityk \citealp{perejon2011}, or Datafit \citealp{cheng2015}}. Software accessibility and reproducibility may be one reason why thermogravimetric analysis has not yet been widely adopted by functional ecologists, despite being previously used to identify plant species' recalcitrance \citetext{for example in marine and coastal macrophytes \citealp{trevathan-tackett2015}, and eucaplyts \citealp{orfao2001}}. \\
\\
The \verb|deconvolve| package provides an open-source set of functions to perform this deconvolution. Although the nonlinear mixture model used for peak separation at the core of this package could be used for many different purposes, \verb|deconvolve| aims to provide context specific guidelines related to use of this model for thermal decay curve analysis and carbon component estimation, in order to maximise its utility and ease of uptake for researchers interested in this method.

@@

<<>>=
library(deconvolve)
head(juncus)
@

@@

  x <- seq(200, 700)
  h1 <- deconvolve::fs_function(x, 0.004, -0.25, 400, 60)
  h2 <- deconvolve::fs_function(x, 0.006, -0.25, 400, 60)
  h3 <- deconvolve::fs_function(x, 0.008, -0.25, 400, 60)
  h4 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)

  s1 <- deconvolve::fs_function(x, 0.010, -0.55, 400, 60)
  s2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
  s3 <- deconvolve::fs_function(x, 0.010, 0.25, 400, 60)
  s4 <- deconvolve::fs_function(x, 0.010, 0.55, 400, 60)

  p1 <- deconvolve::fs_function(x, 0.010, -0.25, 350, 60)
  p2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
  p3 <- deconvolve::fs_function(x, 0.010, -0.25, 450, 60)
  p4 <- deconvolve::fs_function(x, 0.010, -0.25, 500, 60)

  w1 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 30)
  w2 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 60)
  w3 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 90)
  w4 <- deconvolve::fs_function(x, 0.010, -0.25, 400, 120)

@@

All analyses were conducted within the statistical computing environment, R \citep{R}, and data and R code for this paper are available on the package Github (\url{https://github.com/smwindecker/deconvolve/}. In order to aid in the reproducibility of this work, our code was written using a \verb|remake| framework \citep{remake}. This allows others to readily reproduce our work by calling \verb|remake()| in R.

@@

\section*{Quality control}
All the functions of \verb|deconvolve| were tested to see if they produced the desired output. ?... The structure of the package successfully passed the \verb|CRAN R CMD| check and the results from this check can be found on CRAN.

@@

\section*{Additional system requirements}
An internet connection is required to install the \verb|deconvolve| package.

@@

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] \url{https://github.com/smwindecker/deconvolve/}
	\item[Persistent identifier:] e.g. DOI, handle, PURL, etc.
	\item[Licence:] Open license under which the software is licensed.
	\item[Date published:] dd/mm/yy
\end{description}

@@

This package was designed with both the user and developer in mind. There are several vignettes available with the package and on the package website (\url{https://smwindecker.github.io/deconvolve/}) facilitating exploration of package functionality. For those that wish to contribute to the package, it is hosted on Github, and they can log issues via the issues tracker (\url{https://github.com/smwindecker/deconvolve/issues}) or submit a pull request to add functionality to the package.

>>>>

\section*{Title}
mixchar: An R package for the deconvolution of thermal decay curves

@@

\section*{Introduction}
Plant cell wall biomass is composed of a range of different types of carbon. Ecologists can use these proportions of biomass carbon as functional traits, enabling us to make generalisations about species' effects on ecosystem processes such as litter decomposition, which links plant biomass to the global carbon cycle \citep{cornwell2008}. Biofuels researchers use proportions of biomass carbon types to estimate kinetic decay parameters of species' tissue. Traditional methods for calculation of lignocellulosic biomass involve wet chemistry assays for carbon component analysis are time-consuming and adversely impact the environment through use of sulfuric acid and acetic anhydride, among other chemicals. Thermogravimetric analysis (TGA) is an alternative method, already in use among biofuels researchers, to approximate these carbon compounds from mass loss data obtained by heating a biomass sample (in a $N_2$ environment, termed pyrolysis). \\
\\
Mass loss during pyrolysis can be regarded as the sum of the degradation of the main components of the sample \textemdash hemicelluloses, cellulose, and lignin \citep{hu2016,cheng2015,perejon2011,orfao2001,muller-hagedorn2007}. Therefore, the multi-peaked rate of mass loss curve (derivative of mass loss curve) can be mathematically separated, or deconvolved, with a mixture model into individual peaks \textemdash each representing a single primary component. This method has been validated by studies comparing estimates to experimental measurements \citep{yang2006}. Plant trait measurement is guided by the principle of standardised, widely reproducible methods \citep{perez-harguindeguy2013}, but much of the published literature use commercial software to deconvolve the rate of mass loss curve \citetext{for example OriginPro \citealp{chen2017}, PeakFit \citealp{perejon2011}, Fityk \citealp{perejon2011}, or Datafit \citealp{cheng2015}}. Software accessibility and reproducibility may be one reason why thermogravimetric analysis has not yet been widely adopted by functional ecologists, despite being previously used to identify plant species' recalcitrance \citetext{for example in marine and coastal macrophytes \citealp{trevathan-tackett2015}, and eucaplyts \citealp{orfao2001}}. \\
\\
The \verb|mixchar| package provides an open-source set of functions to perform this deconvolution. Although the nonlinear mixture model used for peak separation at the core of this package could be used for many different purposes, \verb|mixchar| aims to provide context specific guidelines related to use of this model for thermal decay curve analysis and carbon component estimation, in order to maximise its utility and ease of uptake for researchers interested in this method.

@@

<<>>=
library(mixchar)
head(juncus)
@

@@

  x <- seq(200, 700)
  h1 <- mixchar::fs_function(x, 0.004, -0.25, 400, 60)
  h2 <- mixchar::fs_function(x, 0.006, -0.25, 400, 60)
  h3 <- mixchar::fs_function(x, 0.008, -0.25, 400, 60)
  h4 <- mixchar::fs_function(x, 0.010, -0.25, 400, 60)

  s1 <- mixchar::fs_function(x, 0.010, -0.55, 400, 60)
  s2 <- mixchar::fs_function(x, 0.010, -0.25, 400, 60)
  s3 <- mixchar::fs_function(x, 0.010, 0.25, 400, 60)
  s4 <- mixchar::fs_function(x, 0.010, 0.55, 400, 60)

  p1 <- mixchar::fs_function(x, 0.010, -0.25, 350, 60)
  p2 <- mixchar::fs_function(x, 0.010, -0.25, 400, 60)
  p3 <- mixchar::fs_function(x, 0.010, -0.25, 450, 60)
  p4 <- mixchar::fs_function(x, 0.010, -0.25, 500, 60)

  w1 <- mixchar::fs_function(x, 0.010, -0.25, 400, 30)
  w2 <- mixchar::fs_function(x, 0.010, -0.25, 400, 60)
  w3 <- mixchar::fs_function(x, 0.010, -0.25, 400, 90)
  w4 <- mixchar::fs_function(x, 0.010, -0.25, 400, 120)

@@

All analyses were conducted within the statistical computing environment, R \citep{R}, and data and R code for this paper are available on the package Github (\url{https://github.com/smwindecker/mixchar/}. In order to aid in the reproducibility of this work, our code was written using a \verb|remake| framework \citep{remake}. This allows others to readily reproduce our work by calling \verb|remake()| in R.

@@

\section*{Quality control}
All the functions of \verb|mixchar| were tested to see if they produced the desired output. ?... The structure of the package successfully passed the \verb|CRAN R CMD| check and the results from this check can be found on CRAN.

@@

\section*{Additional system requirements}
An internet connection is required to install the \verb|mixchar| package.

@@

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] \url{https://github.com/smwindecker/mixchar/}
	\item[Persistent identifier:] e.g. DOI, handle, PURL, etc.
	\item[Licence:] Open license under which the software is licensed.
	\item[Date published:] dd/mm/yy
\end{description}

@@

This package was designed with both the user and developer in mind. There are several vignettes available with the package and on the package website (\url{https://smwindecker.github.io/mixchar/}) facilitating exploration of package functionality. For those that wish to contribute to the package, it is hosted on Github, and they can log issues via the issues tracker (\url{https://github.com/smwindecker/mixchar/issues}) or submit a pull request to add functionality to the package.
